Supporting Information

### 2016-12-06 portfolio/text/ms.Rmd
Create and add IFQ figure to supplement

The Alaskan halibut and sablefish fisheries were rationalized in 199X --- they
switched from XX to a individual fishery quota (IFQ) system. We refit our models
allowing all effects to vary separately before and after 19XX for strategies
involving these permits (i.e. treating them as separate strategies). Variability
was reduced by ~25% (XX--XX 95% CI) after the introduction of these IFQs
compared to before for individuals with only a halibut or sablefish permit (Fig.
SX). The cost of changing fished species diversity for an individual in terms of
the effect on revenue variability increased after the introduction of IFQs for
all strategies, and especially for individuals fishing only halibut and
sablefish (Fig. SX).

>>>>

The Alaskan halibut and sablefish fisheries were rationalized in 199X --- they
switched from XX to a individual fishery quota (IFQ) system. We refit our
models allowing all effects to vary separately before and after 19XX for
strategies involving these permits (i.e. treating them as separate strategies).
Variability was reduced by ~25% (XX--XX 95% CI) after the introduction of these
IFQs compared to before for individuals with only a halibut or sablefish permit
(Fig. S\ref{fig:ifq}A). The cost of changing fished species diversity for an
individual in terms of the effect on revenue variability increased after the
introduction of IFQs for most strategies, and especially for individuals fishing
only halibut and sablefish (Fig. S\ref{fig:ifq}B).

### 2016-12-06 portfolio/text/supp.Rnw
Create and add IFQ figure to supplement

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/itq-combined.pdf}
\caption{The effect of IFQs (individual fishing quotas) on model estimates. (A)
  Posterior density of the ratio between strategy-level estimates of
  standardized revenue variability ($\gamma_{0j}$'s) after the introduction of
  IFQs vs.\ before the introduction of IFQs. (B) Estimates (medians) of the
  effect of generalizing (increasing species diversity) on variability
  ($\gamma_{1j}$'s) for the full model (``Grouped'') compared to a model where
  separate effects are estimated before and after IFQs were introduced (``IFQ
  split''). Pattern looks similar for the effect of specializing on variability
  ($\gamma_{2j}$'s) and is not shown.}
\label{fig:ifq}
\end{center}
\end{figure}
